Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-04-18 finalReportPres.tex
Updated NN Algorithm Section of Presentation

      \foreach \l [count=\i] in {1,2,n}
      \draw [<-] (input-\i) -- ++(-1,0)
      node [above, midway] {$\mathbf{e}_{k,\l}$};

      \foreach \l [count=\i] in {1,2,3,\mbox{$\bar{n}$}}
      \node [above] at (hidden-\i.north) {$\sigma_{\l}$};

      \foreach \l [count=\i] in {1,m}
      \draw [->] (output-\i) -- ++(1,0)
      node [above, midway] {$\hat{u}_{a,k}^{(\l)}$};

@@

      \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}_a$};
      \draw[->,ultra thick](3,-2.5) to[bend left] (3,1.6);

    \end{tikzpicture}
    \caption{Actor neural network structure for approximating control input.}
    \label{fig:nnActor}
		\end{figure}
\end{frame}

@@

\todo[inline]{Use generic input and output symbols instead of my own symbols that I used to inputs (error) and outputs (control inputs) }
  Therefore, approximated actor signal can be written as:
\begin{align}
  \label{eq:approximatePolicyActorWeights}
    \hat{\mathbf{u}}_{a,k} = \mathbf{W}_a^T\bm{\sigma}(\mathbf{e}_k),
  \end{align}
%
where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{\bar{n}}$ with $\bar{n} = n(n+1)/2$ and components of weight matrix ${\bf W}_a$ shown in Fig.~\ref{fig:nnActor} are given by %
%
\begin{align*}
  {\bf W}_a = 
  \begin{bmatrix}
    w_a^{1,1} &  w_a^{1,2} & \ldots &w_a^{1,m}\\
    w_a^{2,1} & w_a^{2,2}& \ldots &w_a^{1,m}\\
    \vdots & \ddots & \ldots &\vdots\\
    w_a^{\bar{n},1} & w_a^{\bar{n},2}& \ldots &w_a^{\bar{n},m}
  \end{bmatrix}.
\end{align*}
%

Now take $\eta$ data points and form the set of linear equations as: %
%
\begin{align*}
&  \bm{\sigma}^T(\mathbf{e}_k) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k}^{[d]}\right)^T\\
 & \bm{\sigma}^T(\mathbf{e}_{k+1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+1}^{[d]}\right)^T\\
                                            &\vdots \\
 & \bm{\sigma}^T(\mathbf{e}_{k+\eta-1}) \mathbf{W}_a  \approx     \left(\mathbf{u}_{a,k+\eta-1}^{[d]}\right)^T  
\end{align*}
%
\end{frame}

\begin{frame}
  In compact form:
  \begin{align*}
    \bm{\Sigma}\mathbf{W}_a \approx  \mathbf{U}^{[d]},\qquad\text{with}
    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
  \end{align*}
  %
  $\mathbb{R}^{\eta\times\bar{n}}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf e}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf u}_{a,\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$

  Let $\bm{\Sigma}\mathbf{W}_a\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta_a$ can be written as:
  \begin{align*}
    \delta_a = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
  \end{align*}

Actor weight ${\bf W}_a$ can then be found minimizing the sum--of--square error $\delta_a$ defined by %
%
\begin{align*}
  \delta_a = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W}_a)\right].
\end{align*}
%
Taking the derivative of $\delta_a$ with respect to ${\bf W}_a$ yields 
%
\begin{align}
  \frac{\partial\delta_a}{\partial\mathbf{W}_a} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a
  \label{eq:actorWeightsGradient}
\end{align}
%

@@

  Setting $\frac{\partial\delta_a}{\partial\mathbf{W}_a}$ to zero yeilds
  \begin{align*}
    {\bf W}_a = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
  \end{align*}

$\bullet$ Actor weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:

\begin{multline}
  \mathbf{W}_a^{(r+1)} = \mathbf{w}_a^{(r)} - \ell_a\frac{\partial\delta_a}{\partial\mathbf{W}_a}= \mathbf{W}_a^{(r)} - \ell_a\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}_a^{(r)}\right)\\
  = \mathbf{w}_a^{(r)}-\ell_a \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}_a^{(r)} - \mathbf{U}^{[d]}\right)
  \label{eq:actorWeightUpdate}
\end{multline}

\todo[inline]{In your case, there is no actor neural network, I implemented generic reinforcement learning structures using actor critic neural network structure}

>>>>

      \foreach \l [count=\i] in {1,2,n}
      \draw [<-] (input-\i) -- ++(-1,0)
      node [above, midway] {$\mathbf{x}_{\l}$};

      \foreach \l [count=\i] in {1,2,3,p}
      \node [above] at (hidden-\i.north) {$\sigma_{\l}$};

      \foreach \l [count=\i] in {1,m}
      \draw [->] (output-\i) -- ++(1,0)
      node [above, midway] {${y}_{\l}$};

@@

      \node [align=center, below] at (3,-2.5) {Weight \\ $\mathbf{W}$};
      \draw[->,ultra thick](3,-2.5) to[bend left] (3,1.6);

    \end{tikzpicture}
    \caption{Neural network structure for approximating system behavior}
    \label{fig:nnActor}
		\end{figure}
\end{frame}

@@

  Therefore, approximated output signal can be written as:
\begin{align}
  \label{eq:approximatePolicyActorWeights}
    \mathbf{y} = \mathbf{W}^T\bm{\sigma}(\mathbf{x}),
  \end{align}
%
where $\bm{\sigma}:\mathbb{R}^n\to\mathbb{R}^{p}$ with components of weight matrix ${\bf W}$ shown in Fig.~\ref{fig:nnActor} are given by %
%
\begin{align*}
  {\bf W} = 
  \begin{bmatrix}
    w^{1,1} &  w^{1,2} & \ldots &w^{1,m}\\
    w^{2,1} & w^{2,2}& \ldots &w^{1,m}\\
    \vdots & \ddots & \ldots &\vdots\\
    w^{p,1} & w^{p,2}& \ldots &w^{p,m}
  \end{bmatrix}.
\end{align*}
%

Now take $\eta$ data points and form the set of linear equations as: %
%
\begin{align*}
&  \bm{\sigma}^T(\mathbf{x}_k) \mathbf{W}  \approx     \left(\mathbf{y}_{k}^{[d]}\right)^T\\
 & \bm{\sigma}^T(\mathbf{x}_{k+1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+1}^{[d]}\right)^T\\
                                            &\vdots \\
 & \bm{\sigma}^T(\mathbf{x}_{k+\eta-1}) \mathbf{W}  \approx     \left(\mathbf{y}_{k+\eta-1}^{[d]}\right)^T  
\end{align*}
%
\end{frame}

\begin{frame}
  In compact form:
  \begin{align*}
    \bm{\Sigma}\mathbf{W} \approx  \mathbf{U}^{[d]},\qquad\text{with}
    % \hat{\mathbf{U}} \approx \mathbf{U}^{[d]}, 
  \end{align*}
  %
  $\mathbb{R}^{\eta\times p}\ni \bm{\Sigma} = [\bm{\Sigma}_0,\bm{\Sigma}_1,\ldots,\bm{\Sigma}_{\eta -1}]^T$ with $\bm{\Sigma}_\kappa = \bm{\sigma}^T({\bf x}_{k+\kappa})$ and $\mathbb{R}^{\eta\times m}\ni {\bf U}^{[d]} = [{\bf U}_0,{\bf U}_1,\ldots, {\bf U}_{\eta-1}]^T$ with ${\bf U}_\kappa = \left({\bf y}_{\kappa}\right)^T$ for $\kappa = 0,1,\ldots,\eta-1.$

  Let $\bm{\Sigma}\mathbf{W}\equiv \hat{\mathbf{U}},$ sum-of-squared error, $\delta$ can be written as:
  \begin{align*}
    \delta = \frac{1}{2}\|\mathbf{U}^{[d]} - \hat{\mathbf{U}}\|^2
  \end{align*}

Weight matrix ${\bf W}$ can then be found minimizing the sum--of--square error $\delta$ defined by %
%
\begin{align*}
  \delta = \frac{1}{2}\|{\bf U}^{[d]} - \bm{\Sigma} {\bf W}\|^2  = \frac{1}{2}\mathrm{Tr}\left[({\bf U}^{[d]} - \bm{\Sigma} {\bf W})^T({\bf U}^{[d]} - \bm{\Sigma} {\bf W})\right].
\end{align*}
%
Taking the derivative of $\delta$ with respect to ${\bf W}$ yields 
%
\begin{align}
  \frac{\partial\delta}{\partial\mathbf{W}} = - \bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}
  \label{eq:actorWeightsGradient}
\end{align}
%

@@

  Setting $\frac{\partial\delta}{\partial\mathbf{W}}$ to zero yeilds
  \begin{align*}
    {\bf W} = \left(\bm{\Sigma}^T\bm{\Sigma}\right)^T\bm{\Sigma}^T{\bf U}^{[d]}.
  \end{align*}

$\bullet$ Hidden layer to output layer weight is updated at each policy iteration $r=0,1,\ldots$ using gradient descent approach as:

\begin{multline}
  \mathbf{W}^{(r+1)} = \mathbf{w}^{(r)} - \ell\frac{\partial\delta}{\partial\mathbf{W}}= \mathbf{W}^{(r)} - \ell\left(-\bm{\Sigma}^T\mathbf{U}^{[d]} + \bm{\Sigma}^T \bm{\Sigma}\mathbf{W}^{(r)}\right)\\
  = \mathbf{w}^{(r)}-\ell \bm{\Sigma}^T\left(\bm{\Sigma}\mathbf{W}^{(r)} - \mathbf{U}^{[d]}\right)
  \label{eq:actorWeightUpdate}
\end{multline}
